VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-02 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest version of article

\section{Cavalieri Integral: Clarifying Example}
\label{sec:cav_integral_example}
The example which we present below was taken from \cite{?}. Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is depicted in Fig.~\ref{fig:caval2}.\\
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.3\textwidth]{fig12}
%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
%\label{fig:ex1}
%\end{figure}
\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{fig13.pdf}
\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$. The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:cav_sum}). Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
\label{fig:caval2}
\end{figure}

@@

\section{Left-sided Riemann-Liouville Fractional Integral}
In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
\begin{equation}
_{a'}I_t\, f(t) := \int_{a'}^t f(\tau)~d\tau.
\end{equation}
Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$. It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ to denote our upper integration limit in Eq.~\ref{??}). 
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_0^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_0^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
\begin{equation}
_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
\end{equation}
The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
Eq.~\eqref{eq:frac_integral} reduces to:
\begin{equation}
_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
\end{equation}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{gh.pdf}
\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
}
\label{fig:gandh}
\end{figure}

>>>>

\section{Cavalieri Integral: Clarifying Example}
\label{sec:cav_integral_example}
The example which we present below was taken from \cite{?}. Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is depicted in Fig.~\ref{fig:caval2}.\\
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.3\textwidth]{fig12}
%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
%\label{fig:ex1}
%\end{figure}
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.75\textwidth]{fig13.pdf}
%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$. The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:cav_sum}). Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
%\label{fig:caval2}
%\end{figure}

@@

\section{Left-sided Riemann-Liouville Fractional Integral}
In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
\begin{equation}
_{a'}I_t\, f(t) := \int_{a'}^t f(\tau)~d\tau.
\end{equation}
Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$. It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ to denote our upper integration limit in Eq.~\ref{??}). 
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_{a'}^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_{a'}^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
\begin{equation}
_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
\end{equation}
The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
Eq.~\eqref{eq:frac_integral} reduces to:
\begin{equation}
_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
\end{equation}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{gh.pdf}
\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
solid lines, while the curves plotted wit h dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
}
\label{fig:gandh}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{vis_old.pdf}
\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
}
\label{fig:gandh}
\end{figure}
